Paper NA

### 2017-02-28 Paper_NA_br.tex
No Linked figures

\begin{figure}[ht]
	\centering
	\begin{tabular}{ccc}
		\includegraphics[width=1\textwidth]{figures/map_events_stn_global.png}
	\end{tabular}

@@

During the inversion, all the synthetic seismograms are computed using the regional SEM code RegSEM \citep{cupillard2012regsem} that takes into account effects of oceans, topography/bathymetry, ellipticity, and anelasticity, and where the limits of the computational domain are dealt with using absorbing boundaries. 
The synthetic seismograms associated with regional data (i.e. where both the seismic stations and the earthquake are located within the regional modeling domain) do not require any specific treatment and are computed as in our previous studies using RegSEM \citep[e.g.][]{yuan2014lithospheric}. 
The synthetic seismograms associated with teleseismic data (i.e. where the earthquake and the seismic stations are located outside and inside the regional modeling domain, respectively) are obtained using a two step procedure as proposed by \cite{masson2016box} as follows.

@@

Overall, the additional computational effort to account for teleseismic events consists of one global simulation per teleseismic event. These simulations are done once and for all before the inversion starts.

@@

	\caption{\baselineskip 18pt
	3D isotropic shear wave velocity structure of the continent. Map views are shown from 60 km down to 300 km, shown as variations with respect to the global mean (thick red line in Figure ~\ref{1daverage}). 
	% Labels are: BP, Blake Plateau; NQ, New Quebec Orogen; THO, Trans-Hudson Orogen. State abbreviations are: CO, Colorado; MT, Montana; ND, North Dakota; SD, South Dakota; and WY, Wyoming. 
	% The geological limits of the cratonic crust are indicated as follows: (to be defined when using final figures... 
	}

@@

The tomographic inversion results for $V_S$ and $\xi$ are presented in figures ~\ref{3d-VS,3d-Xi}. We divide the model description and interpretation into two parts, focusing first on the continent-wide structure and then, in more detail, on eastern different regions.

@@

The average of $\xi$ is higher than $1$ (which means that $V_{SH} > V_{SV}$), but lower than the global average, the latter influenced by the strong $\xi > 1$ oceanic signature.
% where shearing is more important. 
Both trends are similar with depth, but the maximum in $\xi$ is slightly deeper than in the global average and the change from $V_{SH} > V_{SV}$ to $V_{SH} < V_{SV}$ is reached at ca. $420km$. {\color{red} This feature was already present in the global model, and perturbations below that depth are <1\% So I dont think the model adds more informations compared to SEMucb}.
Regions showing highest $\xi$ values

@@

Our study confirms the presence of a thick lithospheric root in the craton with faster than average $V_S$ down to $250km$ depth, with highest velocities, ca. $4.8km.s^{-1}$, located at depths shallower than  $150km$ (e.g. Figure~\ref{cratoncross}). 
Laterally, the cratonic root in $V_S$ coincides roughly with precambrian aged crust (see Figure~\ref{3d-VS} at from 60 to 150km deep)
The western edge of the craton follows the RMF, instead of the western breakup line (See the red thin line in Figure~\ref{mapgeol} which coincides with RMF in Canada, but is diverging westward in the U.S.). While the eastern/south-esatern coincides with the Llano-Grenville Front (See the blue thin line in Figure~\ref{mapgeol}). 
The northern part ends at the coastline of the Arctic ocean including the arctic archipelago and Greenland.

@@

These lateral edges are well observed down to $150km$ depth. Below that, the cratonic root retracts toward the center of the archaean continent and is still present beneath Slave, Hearne/Rae and western Superior cratons as shown in Figure~\ref{cratoncrossedge}. 
Everywhere within the craton, a negative gradient of $V_S$ is observed, marking the base of the lithosphere, with a minimum of $\sim 4.6km.s^{-1}$ reached at $\sim 300km$ depth. While the base of the lithosphere (and top of the low velocity zone- LVZ) shows strong topography, the bottom of the LVZ appears largely flat, in particular under the  Slave, Hearne/Rae and western Superior cratons.
As observed in \cite{babuvska1998age,gung2003global,yuan2014lithospheric}, there are large lateral variations  $\xi$ down to $\sim 200km$ depth, with regions of reduced radial anisotropy, in contrast to the more uniform, positive $dln(\xi)$ structure in this depth range in the oceans. Generally, $\xi$ always appear higher than 1. Around 100 km negative $dln(\xi)$ compared to the isotropic case are observed in Mexico, at the southern part of Florida, the southern part of the Superior craton comprising the Mid Continental rifting, the southern part of the Granit Rhyiolite Province comprising the Failed Rifting area and finally beneath Baffin Island.

>>>>

\begin{figure}[p]
	\centering
	\begin{tabular}{ccc}
		\includegraphics[width=1\textwidth]{figures/map_events_stn_global.png}
	\end{tabular}

@@

During the inversion, all the synthetic seismograms are computed using the regional SEM code RegSEM \citep{cupillard2012regsem} that takes into account effects of oceans, topography/bathymetry, ellipticity, and anelasticity, and where the limits of the computational domain (white box around North America in Figure~\ref{injection} and red box in Figure ~\ref{map_evt_stn}) are dealt with using absorbing boundaries. 
The synthetic seismograms associated with regional data (i.e. where both the seismic stations and the earthquake are located within the regional modeling domain) do not require any specific treatment and are computed as in our previous studies using RegSEM \citep[e.g.][]{yuan2014lithospheric}. 
The synthetic seismograms associated with teleseismic data (i.e. where the earthquake and the seismic stations are located outside and inside the regional modeling domain, respectively) are obtained using a two step procedure as proposed by \cite{masson2016box} as follows.

@@

Overall, the additional computational effort to account for teleseismic events consists of one global simulation per teleseismic event. These simulations are done once and for all before the inversion starts. A comparison between regular $SPECFEM3D\_globe$ and ``RegSEM + virtual sources`` synthetics is shown in Figure~\ref{injection}.

@@

	\caption{\baselineskip 18pt
	3D isotropic shear wave velocity structure of the continent. Map views are shown from 60 km down to 300 km, shown as variations with respect to the regional mean (thick red line in Figure ~\ref{1daverage}). 
	% Labels are: BP, Blake Plateau; NQ, New Quebec Orogen; THO, Trans-Hudson Orogen. State abbreviations are: CO, Colorado; MT, Montana; ND, North Dakota; SD, South Dakota; and WY, Wyoming. 
	% The geological limits of the cratonic crust are indicated as follows: (to be defined when using final figures... 
	}

@@

The tomographic inversion results for $V_S$ and $\xi$ are presented in figures \ref{3d-VS} and \ref{3d-Xi} respectvely. 
We divide the model description and interpretation into two parts, focusing first on the continent-wide structure and then, in more detail, on eastern different regions.

@@

The average of $\xi$ is higher than $1$ (which means that $V_{SH} > V_{SV}$), but lower than the global average, the latter influenced by the strong $\xi > 1$ oceanic signature.
% where shearing is more important. 
Both trends are similar with depth, but the maximum in $\xi$ is slightly deeper than in the global average and the change from $V_{SH} > V_{SV}$ to $V_{SH} < V_{SV}$ is reached at ca. $420km$.

{\color{red} This feature was already present in the global model, and perturbations below that depth are <1\% So I dont think the model adds more informations compared to SEMucb}.

I am on this part..

@@

Our study confirms the presence of a thick lithospheric root in the craton with faster than average $V_S$ down to $250km$ depth, with highest velocities, ca. $4.8km.s^{-1}$, located at depths shallower than  $150km$ (e.g. Figure~\ref{cratoncross}). 
Laterally, the cratonic root in $V_S$ coincides roughly with precambrian aged crust (see Figure~\ref{3d-VS} from 60 to 150km deep)
The western edge of the craton follows the RMF (black thick dashed line in Figure \ref{mapgeol}), instead of the western breakup line (See the red thin line in Figure~\ref{mapgeol} which coincides with RMF in Canada, but is diverging westward in the U.S.). While the eastern/south-esatern coincides with the Llano-Grenville Front (See the blue thin line in Figure~\ref{mapgeol}). 
The northern part ends at the coastline of the Arctic ocean including the arctic archipelago and Greenland.

@@

These lateral edges are well observed down to $150km$ depth. Below that, the cratonic root retracts toward the center of the archaean continent and is still present beneath Slave, Hearne/Rae and western Superior cratons as shown in Figure \ref{cratoncrossedge}. 
Everywhere within the craton, a negative gradient of $V_S$ is observed, marking the base of the lithosphere, with a minimum of $\sim 4.6km.s^{-1}$ reached at $\sim 300km$ depth. 
While the base of the lithosphere (and top of the low velocity zone- LVZ) shows strong topography, the bottom of the LVZ appears largely flat, in particular under the  Slave, Hearne/Rae and western Superior cratons.

As observed in \cite{babuvska1998age,gung2003global,yuan2014lithospheric}, there are large lateral variations  $\xi$ down to $\sim 200km$ depth, with regions of reduced radial anisotropy, in contrast to the more uniform, positive $dln(\xi)$ structure in this depth range in the oceans (See figure \ref{3d-Xi}. 
Below 250km, it is interesting to note that there is a large band of positive anomaly crossing the whole continent (across the US), making the connection between the Pacific and Atlantic mantles.

Generally, $\xi$ always appear higher than 1. 
Except around 100 km, negative absolute values of $\xi$ (lower than -$1\%$) are observed in Mexico, at the southern part of Florida, the southern part of the Superior craton comprising the Mid Continental rifting, the southern part of the Granit Rhyiolite Province comprising the Failed Rifting area and finally beneath Baffin Island.
